Monitoring growth of miR34a asRNA overexpressings cells under conditions of starvation.

### 2017-10-31 inst/growthStarvation/growthStarvation.Rmd
spelling mistake fixed in commited file

#Introduction
As p53 is a well-known regulator of senescence and apoptosis and has been shown to specifically importatnt under conditions of cellular stress, such as starvation. Therefore, we investigated whether overexpression of miR34a AS affects growth rate under normal and starvation conditions by measuring changes in confluency over time.

>>>>

#Introduction
As p53 is a well-known regulator of senescence, growth, and apoptosis and has been shown to specifically important under conditions of cellular stress, such as starvation. Therefore, we investigated whether overexpression of miR34a AS affects growth rate under normal and starvation conditions by measuring changes in confluency over time.
